Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training and Inference with GPUs

### 2020-12-26 NEUROC/sec4-experiments.tex
fix inferring的表达错误

With the sampling techniques, GNNs were trained and inferred in a mini-batch manner.
%
Each epoch was decomposed into many batches.
%
In each batch, PyG only sent the sampled subgraph to the GPU to train or inference.
%
The batch size determined the size of the sampled subgraph.
%
Thus, it affected the accuracy, training/inference time, and memory usage simultaneously.

@@

Among the two sampling methods, the performance of the cluster sampler was stabler than the neighbor sampler.
%
With the cluster sampler, the test accuracy of different GNNs was very close to the accuracy of full-batch training.
%
With the neighbor sampler, the test accuracy of different GNNs showed more obvious differences.

>>>>

With the sampling techniques, GNNs were trained and performed inference in a mini-batch manner.
%
Each epoch was decomposed into many batches.
%
In each batch, PyG only sent the sampled subgraph to the GPU to train or inference.
%
The batch size determined the size of the sampled subgraph.
%
Thus, it affected the accuracy, training/inference time, and memory usage simultaneously.

@@

Among the two sampling methods, the performance of the cluster sampler was more stable than the neighbor sampler.
%
With the cluster sampler, the test accuracy of different GNNs was very close to the accuracy of full-batch training.
%
With the neighbor sampler, the test accuracy of different GNNs showed more obvious differences.
